Inferring neural networks from fluorescent calcium imaging using partial correlation and sample weighting

### 2014-06-05 article.tex
Speak about pca noise filtering
Merge paragraph
put details in a footnote

Since the partial correlation is a symmetric, the causal mechanism behind the
interaction ($A$ directly causes $B$, $B$ directly causes $A$ or both ) can't
be infered. Moreover, two other causal mechanisms might be implied while having
a non-zero partial coefficient: (i) a pair of variables is induced by a
common (hidden) variable; (ii) $A$ (respectively $B$) is conditionally
correlated to a hidden variable affecting $B$ (resp. $A$)
\cite{de2004discovery}.

% Introduce a custom solution to make the Y matrix asymmetric
% Introduce directivity
In our last submission in hope to improve performance, some causal information
(directivity of the links) were added by stacking the partial correlation score
matrix with an pairwise activation heuristics. This method computes an anti-symmetric
activation score $z_{ij}$ based the variation of fluorescence signal of a neuron
$j$ due to a neuron $i$ over all timesteps:
\[
z_{ij} = \sum_{t=1}^n I(X_{t+1,j} - X_{t, i} \in [f_1, f_2]) -  I(X_{t+1,i} - X_{t, j} \in [f_1, f_2])
\]
where $f_1$ and $f_2$ are parameters of the method and $I$ is the
indicator function.

@@

>>>>

% Introduce a custom solution to make the Y matrix asymmetric
% Introduce directivity
Since the partial correlation is a symmetric, the causal mechanism behind the
interaction ($A$ directly causes $B$, $B$ directly causes $A$ or both ) can't
be inferred.\footnote{Also note that two other causal mechanisms might be
implied while having a non-zero partial coefficient: (i) a pair of variables
is induced by a common (hidden) variable; (ii) $A$ (respectively $B$) is
conditionally correlated to a hidden variable affecting $B$ (resp. $A$)
\cite{de2004discovery}.} \cite{de2004discovery}.
In our last submission in hope to improve performance, some causal information
(directivity of the links) were added by stacking the partial correlation score
matrix with an pairwise activation heuristics. This method computes an anti-symmetric
activation score $z_{ij}$ based the variation of fluorescence signal of a neuron
$j$ due to a neuron $i$ over all timesteps:
\[
z_{ij} = \sum_{t=1}^n I(X_{t+1,j} - X_{t, i} \in [f_1, f_2]) -  I(X_{t+1,i} - X_{t, j} \in [f_1, f_2])
\]
where $f_1$ and $f_2$ are parameters of the method and $I$ is the
indicator function.

@@

Finally since there is a high correlation between neurons, we made a
low-rank hypothesis and perform noise filtering through a principal component
approach [TODO cite]. From the $p$ eigen vectors, we only kept the $80\%$ of
those which have the largest eigen value.
